A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-31 paper.tex

\begin{abstract}
We give a complete classification of supersymmetric twists of super Yang-Mills theories with matter in all dimensions.  Super Yang-Mills theories can be modelled classically using the BV formalism; we construct the supersymmetry algebra action using the language of $L_\infty$ algebras, then for each class of square-zero supercharge we give a description of the corresponding twisted theory in terms of partially holomorphic versions of Chern-Simons and BF theory. 
\end{abstract}

@@

>>>>

\begin{abstract}
We give a complete classification of twists of supersymmetric Yang-Mills theories with in dimensions~$2\leq n \leq 10$.
We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action by the supersymmetry algebra using the language of $L_\infty$ algebras.
For each class of square-zero supercharges in the supersymmetry algebra, we give a description of the corresponding twisted theory in terms of partially holomorphic and topological versions of Chern-Simons and $BF$ theory. 
\end{abstract}

@@

\subsection*{Applications to quantization and a relationship to factorization algebras}
\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}

The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
